Probing the Deuteron at Very Large Internal Momenta

### 2020-10-14 MY_PUBLICATIONS/PRL/FINAL_DRAFT/PRL_Submission/prl_response/prl_reply/MARKED/ms_revised_v3.tex
updated PRL to reduce wordcount

simulation program, SIMC \cite{PhysRevC.64.054610} (see Supplemental Material). Additional $^{1}\mathrm{H}(e,e'p)$ data were also taken at three other kinematic settings that covered the SHMS momentum acceptance range for the deuteron and were used for spectrometer optics optimization, 

@@

\indent The kinematics of the recoiling neutron was reconstructed using energy-momentum conservation. The recoil momentum is defined as $\vec{p_{\mathrm{r}}} = \vec{q} - \vec{p_{\mathrm{f}}}$,
and the nuclear binding (or ``missing'') energy as $E_{\mathrm{m}} = \omega - T_{p} - T_{\mathrm{r}}$, where $\vec{p_{\mathrm{f}}}$ is the final proton momentum, $\vec{q}$ is the
3-momentum transfer and $T_{p}$ is the final proton kinetic energy. The recoil particle kinetic energy, $T_{\mathrm{r}}$, is calculated from the electron and proton
4-momentum vectors assuming an exclusive three-body final state with a recoiling neutron.\\

@@

are well known,  a cut to restrict the HMS solid angle acceptance to events that passed directly through the collimator and not by re-scattering from the collimator edges, a ``missing''

@@

originated from the same reaction vertex at the target (see Supplemental Material). \\

@@

over the kinematic bin. The systematic uncertainties associated with the radiative and bin-centering corrections were investigated using the Laget PWIA and FSI models but negligible effects on the cross sections were found (see Supplemental Material).

@@

$E_{\mathrm{f}}$ is the final proton energy, $f_{\mathrm{rec}}\equiv \frac{2p_{\mathrm{f}}^{2}E_{\mathrm{r}}}{2p_{\mathrm{f}}^{2}E_{\mathrm{r}} - (q^{2} - (p_{\mathrm{f}}^{2} + p_{\mathrm{r}}^{2}))E_{\mathrm{f}}}$

@@

The MS calculations used the FF parametrization of Ref. \cite{PhysRevC.70.068202} while the JML calculations used the conventional dipole parametrization for the proton and neutron magnetic FF, the Galster \cite{Galster:1971} parametrization
for the neutron electric FF, and the results from the Hall A experiment of Ref. \cite{PhysRevLett.88.092301} for the proton electric FF parametrization. The JVO calculations used two different FF parametrizations (GKex05 \cite{PhysRevC.66.045501}, AMT \cite{PhysRevC.76.035205}) where a difference of $\sim5.8-6.6 \%$ was found between the respective
JVO reduced cross sections. Figure \ref{fig:fig1} shows the results using only the GKex05 parametrization. \\

@@

%---include references that are not mentioned in the main text
%---but are included in the supplemental material
%---cite supp. material as follows:  (See Supplemental Material) after description of the topic being discussed.
%\nocite{COSY}
%\nocite{barlow2002systematic}
%\nocite{barlow2017}

>>>>

simulation program, SIMC \cite{PhysRevC.64.054610}\cite{cyero_phdthesis}. Additional $^{1}\mathrm{H}(e,e'p)$ data were also taken at three other kinematic settings that covered the SHMS momentum acceptance range for the deuteron and were used for spectrometer optics optimization, 

@@

%\indent The kinematics of the recoiling neutron was reconstructed using energy-momentum conservation. The recoil momentum is defined as $\vec{p_{\mathrm{r}}} = \vec{q} - \vec{p_{\mathrm{f}}}$,
%and the nuclear binding (or ``missing'') energy as $E_{\mathrm{m}} = \omega - T_{p} - T_{\mathrm{r}}$, where $\vec{p_{\mathrm{f}}}$ is the final proton momentum, $\vec{q}$ is the
%3-momentum transfer and $T_{p}$ is the final proton kinetic energy. The recoil particle kinetic energy, $T_{\mathrm{r}}$, is calculated from the electron and proton
%4-momentum vectors assuming an exclusive three-body final state with a recoiling neutron.\\

@@

are well known,  a cut to restrict the HMS solid angle acceptance to events that passed directly through the collimator and not by re-scattering from the collimator edges, a reconstructed binding

@@

originated from the same reaction vertex at the target (see online Supplemental Material). \\

@@

over the kinematic bin. The systematic uncertainties associated with the radiative and bin-centering corrections were investigated using the Laget PWIA and FSI models but negligible effects
on the cross sections were found (see online Supplemental Material).

@@

($E_{\mathrm{f}}, p_{\mathrm{f}}$) are the final proton energy and momentum, respectively, $f_{\mathrm{rec}}\equiv \frac{2p_{\mathrm{f}}^{2}E_{\mathrm{r}}}{2p_{\mathrm{f}}^{2}E_{\mathrm{r}} - (q^{2} - (p_{\mathrm{f}}^{2} + p_{\mathrm{r}}^{2}))E_{\mathrm{f}}}$

@@

The calculations use different FF parametrizations which can lead to a 6$\%$ change of the theortical cross section.\\
%----REMOVED ON 10/14/2020----------
%The MS calculations used the FF parametrization of Ref. \cite{PhysRevC.70.068202} while the JML calculations used the conventional dipole parametrization for
%the proton and neutron magnetic FF, the Galster \cite{Galster:1971} parametrization
%for the neutron electric FF, and the results from the Hall A experiment of Ref. \cite{PhysRevLett.88.092301} for the proton electric FF parametrization.
%The JVO calculations used two different FF parametrizations (GKex05 \cite{PhysRevC.66.045501}, AMT \cite{PhysRevC.76.035205}) where a
%difference of $\sim5.8-6.6 \%$ was found between the respective
%JVO reduced cross sections. Figure \ref{fig:fig1} shows the results using only the GKex05 parametrization. \\

@@

%---include references that are not mentioned in the main text
%---but are included in the supplemental material
%---cite supp. material as follows:  (See Supplemental Material) after description of the topic being discussed.
%\nocite{COSY}
\nocite{barlow2002systematic}
\nocite{barlow2017}

### 2020-10-14 MY_PUBLICATIONS/PRL/FINAL_DRAFT/PRL_Submission/prl_response/prl_reply/supplemental/MARKED/supp_revised.tex
updated PRL to reduce wordcount

energy cut around the deuteron binding energy ($\sim$2.2 MeV) using the missing energy formula described in the Letter, where the
recoiling system is assumed to be a neutron. The peak is not exactly at the deuteron binding energy because energy loss corrections have not
been applied to the data nor SIMC. Figure \ref{fig:Em_Q2_cuts} (right) shows a kinematical cut made on the 4-momentum transfer at $Q^{2} = 4.5\pm0.5$ (GeV/c)$^{2}$

@@

\includegraphics[scale=0.24]{plots/coin_and_eCal_CUT_80MeV_35deg.png}

@@

\includegraphics[scale=0.24]{plots/collimator_CUT_80MeV_35deg_data.png}

>>>>

energy cut around the deuteron binding energy ($\sim$2.2 MeV) using the missing energy formula, $E_{\mathrm{m}} = \omega - T_{p} - T_{\mathrm{r}}$, where
$\vec{p_{\mathrm{f}}}$ is the final proton momentum, $\vec{q}$ is the 3-momentum transfer and $T_{p}$ is the final proton kinetic energy. The recoil particle kinetic energy,
$T_{\mathrm{r}}$, is calculated from the electron and proton 4-momentum vectors assuming an exclusive three-body final state with a recoiling neutron.
The peak is not exactly at the deuteron binding energy because energy loss corrections have not been applied to the data nor SIMC. \\
\indent Figure \ref{fig:Em_Q2_cuts} (right) shows a
kinematical cut made on the 4-momentum transfer at $Q^{2} = 4.5\pm0.5$ (GeV/c)$^{2}$

@@

\includegraphics[scale=0.22]{plots/coin_and_eCal_CUT_80MeV_35deg.png}

@@

\includegraphics[scale=0.22]{plots/collimator_CUT_80MeV_35deg_data.png}

### 2020-10-14 MY_PUBLICATIONS/PRL/FINAL_DRAFT/PRL_Submission/prl_response/prl_reply/supplemental/supp_original.tex
updated PRL to reduce wordcount

\noindent Figures \ref{fig:fig3}-\ref{fig:fig7} show the event selection cuts for data (blue hatched) and SIMC (red data points) for the deuteron 80 MeV/c kinematic setting at $\theta_{nq}=35\pm5^{\circ}$.

@@

\includegraphics[scale=0.30]{plots/Em_and_Q2_CUT_80MeV_35deg.png}

@@

\label{fig:fig6}

@@

\caption{Same as Fig. \ref{fig:fig6}, but for simulation.}
\label{fig:fig7}

>>>>

\noindent Figures \ref{fig:fig1}-\ref{fig:fig5} show the event selection cuts for data (blue hatched) and SIMC (red data points) for the deuteron 80 MeV/c kinematic setting at $\theta_{nq}=35\pm5^{\circ}$.

@@

\includegraphics[scale=0.35]{plots/Em_and_Q2_CUT_80MeV_35deg.png}

@@

@@

\caption{Same as Fig. \ref{fig:fig4}, but for simulation.}
\section{\large Deuteron Kinematic Distributions }
\noindent Figures \ref{fig:fig8} and \ref{fig:fig9} show the fundamental kinematic variable distributions for each of the central missing momentum settings at $\theta_{nq}=35^{\circ}$ and $45^{\circ}$.
The data has been normalized by the total charge and corrected for the inefficiencies described in the Letter. Radiative and bin-centering corrections have not been applied for these plots.
The same event selection cuts mentioned in the previous sections were applied (including the $Q^{2}$ cut), with the exception of the $Q^{2}$ distribution itself.
Only the first dataset (out of 2) for the 580 and (out of 3) for the 750 MeV/c settings are shown. 
\includegraphics[scale=0.4]{plots/d2_kin_thnq35.png}
\caption{Deuteron kinematic distributions for the 80 (blue), 580 (set1, red) and 750 (set1, magenta) MeV/c cental missing momentum settings at $\theta_{nq}=35^{\circ}$.}
\includegraphics[scale=0.35]{plots/d2_kin_thnq45.png}
\caption{Same as Fig. \ref{fig:fig8}, but for $\theta_{nq}=45^{\circ}$}

### 2020-10-14 PRL_UTILITIES_CODES/prl_wordcount/ms.tex
updated PRL to reduce wordcount

\documentclass[aps,prl,twocolumn,showpacs,superscriptaddress,groupedaddress,nofootinbib]{revtex4-2}  % for review and submission
\pdfoutput=1 
\usepackage{graphicx}  % needed for figures
\usepackage{ragged2e}
\usepackage{dcolumn}   % needed for some tables
\usepackage{bm}        % for math
\usepackage{amssymb}   % for math
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage{xcolor}
\usepackage{float}
\usepackage{lipsum}
\hypersetup{
    colorlinks,
    linkcolor={blue!80!black},
    citecolor={blue!80!black},
    urlcolor={blue!80!black}
}
\hyphenation{ALPGEN}
\hyphenation{EVTGEN}
\hyphenation{PYTHIA}

@@

Recoil momenta up to $p_{\mathrm{r}}\sim1$ GeV/c have also been probed in a $^{3}\mathrm{He}(e,e'p)$ experiment \cite{PhysRevLett.94.082305,PhysRevLett.94.192302} but at a relatively low momentum transfer of 1.5 (GeV/c)$^{2}$ and at a kinematic region
(Bjorken $x_{\mathrm{Bj}}\sim1$) where the cross section is dominated by final state interactions.\\

@@

%\indent We acknowledge the outstanding support of the staff of the Accelerator and Physics Divisions at Jefferson Lab
%as well as the entire Hall C staff, technicians, graduate students and users who took shifts or contributed
%to the equipment for the Hall C upgrade, making all four commissioning experiments possible. We would also like to
%thank Misak Sargsian, J.M. Laget, Sabine Jeschonnek and J.W. Van Orden for providing the theoretical calculations as well as the useful
%discussions we had on this topic. This work was supported in part by the U.S. Department of Energy (DOE), Office of Science, Office of Nuclear Physics
%under grant No. DE-SC0013620 and contract DE-AC05-06OR23177, the Nuclear Regulatory Commission (NRC) Fellowship
%under grant No. NRC-HQ-84-14-G-0040, the Doctoral Evidence Acquisition (DEA) Fellowship and the Natural Sciences and Engineering Research Council of Canada (NSERC).

%---include references that are not mentioned in the main text
%---but are included in the supplemental material
%---cite supp. material as follows:  (See Supplemental Material) after description of the topic being discussed.
\nocite{COSY}
\nocite{barlow2002systematic}
\nocite{barlow2017}

>>>>

\documentclass[aps,prl,twocolumn,showpacs,superscriptaddress,groupedaddress]{revtex4-2}  % for review and submission
\pdfoutput=1
\usepackage{graphicx}  % needed for figures
\usepackage{ragged2e}
\usepackage{dcolumn}   % needed for some tables
\usepackage{bm}        % for math
\usepackage{amssymb}   % for math
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage{xcolor}
\usepackage{float}
\usepackage{lipsum}
\hypersetup{
    colorlinks,
    linkcolor={blue!80!black},
    citecolor={blue!80!black},
    urlcolor={blue!80!black}
}
\hyphenation{ALPGEN}
\hyphenation{EVTGEN}
\hyphenation{PYTHIA}

@@

Missing momenta up to $\sim1$ GeV/c have also been probed in a $^{3}\mathrm{He}(e,e'p)$ experiment \cite{PhysRevLett.94.082305,PhysRevLett.94.192302} but at a relatively low momentum transfer of 1.5 (GeV/c)$^{2}$ and at a kinematic region
(Bjorken $x_{\mathrm{Bj}}\sim1$) where the cross section is dominated by final state interactions. Due to FSI effects, the measurement of certain missing momentum does not yet guarantee that the initial
bound nucleon with the same momentum is being measured.\\

@@

%\indent We acknowledge the outstanding support of the staff of the Accelerator and Physics Divisions at Jefferson Lab
%as well as the entire Hall C staff, technicians, graduate students and users who took shifts or contributed
%to the equipment for the Hall C upgrade, making all four commissioning experiments possible. We would also like to
%thank Misak Sargsian, J.M. Laget, Sabine Jeschonnek and J.W. Van Orden for providing the theoretical calculations as well as the useful
%discussions we had on this topic. This work was supported in part by the U.S. Department of Energy (DOE), Office of Science, Office of Nuclear Physics
%under grant No. DE-SC0013620 and contract DE-AC05-06OR23177, the Nuclear Regulatory Commission (NRC) Fellowship
%under grant No. NRC-HQ-84-14-G-0040, the Doctoral Evidence Acquisition (DEA) Fellowship and the Natural Sciences and Engineering Research Council of Canada (NSERC).

%---include references that are not mentioned in the main text
%---but are included in the supplemental material
%---cite supp. material as follows:  (See Supplemental Material) after description of the topic being discussed.
%\nocite{COSY}
%\nocite{barlow2002systematic}
%\nocite{barlow2017}
